Computer Science House By-Laws

### 2016-02-27 bylaws.tex

	\item If an Introductory Member fails to meet the requirements, his membership will be revoked. In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements. A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House. Each conditional consists of a set of additional requirements a deadline for completing them. When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness. A conditional member who does not meet these additional requirements forfeits membership.

@@

Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues.

@@

	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee. The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}. An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.

@@

	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote. If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}. Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.

@@

	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members. After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.

@@

	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}. If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level. If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated. This recast process may not be repeated a second time.
	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection. If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors. Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level. If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.

@@

During the academic year, a House member is evaluated by two different processes. The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House. The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year. These processes are separate from each other and should not interfere with one another. Semi-Annual Evaluations Meetings are open only to all current Active Members. All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.

@@

At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process. It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.

@@

The Housing Evaluation process occurs during the academic year. It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director. The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).

@@

All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant. A member’s failure to submit the activity report will result in that member receiving no housing points. Attendance is also required for a member to be evaluated, else they will receive no housing points. Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote. Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.

@@

The participating members, on a member by member basis, review the activity report provided by each member. The participating members may then choose to award one, two, or three housing points to each member. Points are awarded on the basis of contributions to House. Above average members receive three points, average members two points, and below average members one point.

@@

A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year. All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed before the Membership Evaluation occurs. A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.

@@

If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately. If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}). In either case, the member forfeits his ability to be included on the following year’s roster.

@@

A member may be given a conditional to complete as a means of making up for missing requirements. A conditional may be proposed by any member present at the Evaluation and, if it is approved by the Evaluations Director, is then voted on by House. Each conditional consists of a set of additional requirements a deadline for completing them. When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness. A conditional member who does not meet these additional requirements will have failed the evaluation.

>>>>

	\item If an Introductory Member fails to meet the requirements, his membership will be revoked.
		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
		Each conditional consists of a set of additional requirements a deadline for completing them.
		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness. A conditional member who does not meet these additional requirements forfeits membership.

@@

Note: Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member must also pay dues.

@@

	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.

@@

	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.

@@

	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.

@@

	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}.
		If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level.
		If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated.
		This recast process may not be repeated a second time.
	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
		If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors.
		Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level.
		If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.

@@

During the academic year, a House member is evaluated by two different processes.
The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House.
The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
These processes are separate from each other and should not interfere with one another.
Semi-Annual Evaluations Meetings are open only to all current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.

@@

At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.

@@

The Housing Evaluation process occurs during the academic year.
It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director.
The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).

@@

All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant.
A member’s failure to submit the activity report will result in that member receiving no housing points.
Attendance is also required for a member to be evaluated, else they will receive no housing points.
Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote.
Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.

@@

The participating members, on a member by member basis, review the activity report provided by each member.
The participating members may then choose to award one, two, or three housing points to each member.
Points are awarded on the basis of contributions to House.
Above average members receive three points, average members two points, and below average members one point.

@@

A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither Absentee nor Proxy votes are allowed.

@@

A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year.
All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.
These requirements are detailed in Article V under expectations for each category of membership.
These requirements must be completed before the Membership Evaluation occurs.
A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.
House may choose any of the Outcomes for each member.

@@

If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits his ability to be included on the following year’s roster.

@@

A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
Each conditional consists of a set of additional requirements a deadline for completing them.
When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.
